---
title: "607_Assignment3"
author: "IvanTikhonov"
date: "2022-09-11"
output: html_document
---
#1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"



```{r}

data_majors<- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv", header = TRUE, sep = ",")
grep(pattern = 'STATISTICS|DATA', data_majors$Major, value = TRUE, ignore.case = TRUE)

```
There is one major with "data" in the major name. There are two majors with "statistics" in the major name.
#2 Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"

[9] "elderberry"   "lime"         "lychee"       "mulberry" 

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")



```{r}
Strings <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"
[9] "elderberry"   "lime"         "lychee"       "mulberry" 
[13] "olive"        "salal berry"'

newString <- stringr::str_extract_all(Strings, pattern = '[A-Za-z]+.?[A-Za-z]+')
suppressWarnings(GreatJob <- stringr::str_c(newString, collapse = ", "))
```
The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:

#3 Describe, in words, what these expressions will match:
1.(.)\1\1
This will characters that are three times in a row.
2."(.)(.)\\2\\1"
It is will match any four characters that read the same forward and backward.
3.(..)\1
This will match two characters repeated.
4."(.).\\1.\\1"
Match five characters where the first, third and fifth are the same and the second and fourth can be anything.
5."(.)(.)(.).*\\3\\2\\1"
It will match six or more characters where the first three characters are the same as the last three in reverse order.


#4 Construct regular expressions to match words that:
1.Start and end with the same character.
(.)[a-z]*\1
2.Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
([a-z]{2})[a-z*\1]
3.Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
a-z[a-z]\1[a-z]\1[a-z]
```{r}

```

